\documentclass[12pt]{report}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\usepackage{hyperref}

\usepackage{graphicx}
\graphicspath{ {./} }

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[inline]{enumitem}

\usepackage{tikz}
\usetikzlibrary{shapes.multipart}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{prop}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem*{example}{Example}
\newtheorem*{notation}{Notation}
\newtheorem*{cor}{Corollary}
\newtheorem*{rem}{Remark}
\newtheorem*{conj}{Conjecture}

\begin{document}

\title{(Rational) Parking Functions}
\author{Tessa Lelièvre-Osswald\\
    {\small Advisor: Matthieu Josuat-Vergès}\\
    {\small Team: IRIF Combinatorics}}
\date{\today}

\maketitle

\begin{abstract}
    \paragraph{} Introduced in 1966 by Konheim and Weiss
    \cite{ref1}, a (classical) Parking Function is a
    combinatorial structure represented by an integer
    sequence $(a_1, \ldots, a_n)$ such that
    $\#\{i\ |\ a_i \leqslant k\} \geqslant k\ \forall k$.

    \paragraph{} In this article, we will address bijections
    and posets on four types of parking functions :
    classical (also called \emph{integer}), primitive classical,
    rational, and primitive rational.
    Those four types are defined throughout the article.
    
    \paragraph{} Each of these types has been proved
    to be counted by a well-known number -- respectively 
    $(n+1)^{n-1}$, $Cat_n$, $b^{a-1}$, and $Cat_{a,b}$.
    Nevertheless, to the best of our knowledge, the posets
    we will present here have not been exploited on parking
    functions specifically.

    Furthermore, Theorem 8 and its equivalent Conjecture for
    classical parking functions reveal interesting results on
    the number of intervals in those posets.

    \paragraph{} This report goes hand in hand with a Sagemath
    implementation. Notions found in \cite{ref2}, \cite{ref3},
    \cite{ref4}, \cite{ref5}, \cite{ref6}, \cite{ref7},
    \cite{ref8}, and \cite{ref9} are encoded alongside the
    aforementioned posets.
    All of the source code and premade tests can be found
    \href{https://github.com/tessalsifi/ParkingFunctions}{here}
    \footnote{github.com/tessalsifi/ParkingFunctions}.

    \paragraph{} Finally, The notion of Parking Trees defined
    in \cite{ref9} is extended to the rational case, hence
    creating a bijection between rational parking functions and
    Rational Parking Trees.

\end{abstract}

\tableofcontents

\chapter{The integer case}
\input{C1S1.tex}
\input{C1S2.tex}
\input{C1S3.tex}
\input{C1S4.tex}

\chapter{The rational case}

For the whole chapter, we will consider 2 \emph{coprime}
integers $a$ and $b$ (meaning $a$ and $b$ have $1$ as their
greatest common divisor).

\input{C2S1.tex}
\input{C2S2.tex}
\input{C2S3.tex}

\chapter{Trees}

\input{C3S1.tex}
\input{C3S2.tex}

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}